---
title: "Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
subtitle: "Possible factors effecting 2016 election"
author: 
  - Young Suk
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper has been examined possible variables that influenced U.S citizens' choice for the 2016 U.S presidential election. We have found that there exists significantly different opinions regarding gender, wealth, race and age. This is important in a sesne that it shows thought trends as well as crucial decision indicators for voting in U.S.,With further survey at the end of this paper, we are going to explore whether this is happening only in U.S or not."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
```

# Introduction
Religion has been major part of human history around the world, and for many countries, religion is something they heavily rely on even in modern days.For example, European countries such as Spain and Italy which heavily relies on catholic, and there are many middle eastern countries that heavily rely on muslim, islam and hinduism. While it is reported that the number of religious people is declining quickly, religion still has big social influence in many aspects of the society in the United States, and this paper aims to research the social influence of popular religions in the United States and how the opinions of different religions differ in the context of social issues and government policies regarding them.

This research will focus on some social issues in the United States and how opinions of people of different religion differs.


This paper is mainly going to explore possible variables that potentially had impacts on decision regarding the election as well as their analysis. However, making a choice for  which variables affected U.S citizens to lean on Trump side or Clinton side was not easy because there is nothing in this world absolute. Thus, as we mentioned above, we are going to focus on general flows of results instead of defining variables as absolute factors of the demarcation. Following that, this paper has structures: Data, Results, Discussion, Appendix and supplementary survey. 

The dataset was obtained from U.S GSS, and only picked and used the variables that are very related to the subject of this study. Throughout the analysis of relation between the variables and respondents' votes on the election, we could observe that people who had conservative thoughts on equality and welfare preferred Trump, and people who did not preferred Clinton. This may sound obvious considering their parties. In the result session, reader can observe that what specific areas or fields the respondents considered important. We believe that this situation is not only happening in U.S, but it is also happening all over the world. This claim is going to be conducted with supplementary survey session. 


This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.

# Data
```{r, include=FALSE, echo=FALSE}
# Read the reduced and cleaned data, modification done in data-preparation.r file
reduced_data <- read_csv("outputs/data/prepared_gss.csv")
# Change the order of variables for graphing purposes
reduced_data$Family_income <- factor(reduced_data$Family_income, 
                                     levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999", 
                                                "$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))
reduced_data$Immigration <- factor(reduced_data$Immigration, levels = c("Strongly disagree","Disagree", "Neither","Agree","Strongly agree"))
```

The Original data is from survey by US GSS, which contains data of public opinions of USA citizens on various subjects. The data is from 2021 survey which was conducted online due to global pandemic by COVID19. For the purpose of this research, the data related to personal profiles, survey respondants' opinion on government policies and religion has been extracted from the raw survey data.

The religion data has very detailed options that includes religions have very low For the simplicity of this research, protestants and christians were grouped together under chrinstans and all the non-popular religion has been grouped under "other".



```{r fig1,echo=FALSE, fig.cap = "Distribution of survey respondents' age group."}
reduced_data %>%
  drop_na(age_group) %>%
  ggplot(aes(x = age_group, fill = relig)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Age") +
  theme(legend.title = element_blank())
```

```{r fig2, fig.cap= "Distribution of survey respondents' race.", echo = FALSE}
reduced_data %>%
  ggplot(aes(x = race, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Race",
       ) +
  theme(legend.position = "none")
```

```{r fig3, echo = FALSE, fig.cap= "Distribution of survey respondents' gender"}
reduced_data %>%
  ggplot(aes(x = gender, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Gender",
       ) +
  theme(legend.position = "none")
```

```{r fig4, echo=FALSE, fig.cap = "Distribution of religion of survey respondents"}
reduced_data %>%
  ggplot(aes(x = relig, fill = relig)) +
  geom_bar() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Religion",
       ) +
  coord_flip() +
  theme(legend.title = element_blank())
```



\newpage

# Results


# Discussion

## Summary


## Different Opinions between different religions.

## Weaknesses and how we should proceed in the future



\newpage

# appendix


\newpage


# References
Smith, Tom W., Davern, Michael, Freese, Jeremy, and Morgan, Stephen L., General Social Surveys, 1972-2018 [machine-readable data file] /Principal Investigator, Smith, Tom W.; Co-Principal Investigators, Michael Davern, Jeremy Freese and Stephen L. Morgan; Sponsored by National Science Foundation. --NORC ed.-- Chicago: NORC, 2019.

U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.